shorts: An R Package for Modeling Short Sprints

### 2022-06-20 shorts-paper.Rmd
Updated to use {short} 1.2

```{r}
# Since this is a perfect simulation and stats::nls will complain
# we need to add very small noise, or measurement error to the times
set.seed(1667)
rand_noise <- rnorm(nrow(split_times), 0, 10^-5)
split_times$john_time <- split_times$john_time + rand_noise
split_times$jack_time <- split_times$jack_time + rand_noise

john_profile <- model_using_splits(
  distance = split_times$distance,
  time = split_times$john_time
)

@@

sim_df <- sim_df %>%
  mutate(
    TAU = MSS / MAC,
    PMAX = MSS * MAC / 4,
    true_distance = distance + flying_start_distance,
    true_time = predict_time_at_distance(true_distance, MSS, TAU),
    stolen_time = predict_time_at_distance(
      flying_start_distance, MSS, TAU
    ),
    time = true_time - stolen_time
  )

# Add small noise to allow model fit
set.seed(1667)
rand_noise <- rnorm(nrow(sim_df), 0, 10^-5)
sim_df$time <- sim_df$time + rand_noise
```

@@

  time_correction <- model_using_splits_with_time_correction(
    distance = data$distance,
    time = data$time,
    control = nls.control(warnOnly = TRUE)
  )

  distance_correction <- model_using_splits_with_distance_correction(
    distance = data$distance,
    time = data$time,
    control = nls.control(warnOnly = TRUE)
  )

  time_dist_correction <- model_using_splits_with_corrections(
    distance = data$distance,
    time = data$time,
    control = nls.control(warnOnly = TRUE)
  )

>>>>

```{r}
john_profile <- model_using_splits(
  distance = split_times$distance,
  time = split_times$john_time
)

@@

sim_df <- sim_df %>%
  mutate(
    TAU = MSS / MAC,
    PMAX = MSS * MAC / 4,
    true_distance = distance + flying_start_distance,
    true_time = predict_time_at_distance(true_distance, MSS, TAU),
    stolen_time = predict_time_at_distance(
      flying_start_distance, MSS, TAU
    ),
    time = true_time - stolen_time
  )
```

@@

  time_correction <- model_using_splits_with_time_correction(
    distance = data$distance,
    time = data$time
  )

  distance_correction <- model_using_splits_with_distance_correction(
    distance = data$distance,
    time = data$time
  )

  time_dist_correction <- model_using_splits_with_corrections(
    distance = data$distance,
    time = data$time
  )
